\section{Scientific context} 

Molecules are present everywhere in the interstellar medium, even in the diffuse medium where the UV field was believed to destroy them (see for instance \cite{2012ApJ...753L..28L}). In the densest and coldest parts of the ISM (i.e. cold cores) shielded from the interstellar UV field, many molecules are formed and can survive. The formation of these species in the gas-phase has been studied for a long time now. Chemical networks have been built to index all individual reactions and associated rate coefficients that play a role in the determination of the abundances of molecules observed. It was first believed that ion-neutral reactions were the driving mechanism of this chemistry. But with the development of experimental methods allowing for measurements of rate coefficients at low low temperatures in the laboratory, it appeared clear that many neutral-neutral reactions would be crucial at the lowest temperatures (\cite{2010SSRv..156...13W}, \cite{Smith_2011}). Since 2009, with a group of chemists, we have been working on gas-phase networks in order to propose to the community the most complete and accurate data to model the chemistry in the ISM. Up to now, several families have been revisited: 
\begin{itemize}
\item{Nitrogen bearing species (\cite{2013PCCP...1513888D}, \cite{2012PNAS..10910233D}, \cite{2014MNRAS.443..398L}, \cite{2013arXiv1310.4350W}. We in particular studied the reactions involved in the chemistry of N$_2$, HCN and HNC.} 
\item{Carbon bearing species (\cite{Wakelam_2009}, \cite{2014MNRAS.437..930L}, \cite{2015MNRAS.453L..48W}). The main results of these studies were to decrease the predicted abundances of large carbon bearing species and propose a formation scenario for HCCO (recently observed in dense cores by \cite{Ag_ndez_2015}.} 
\end{itemize}
Other families are currently being reviewed such as Sulphur-bearing molecules and C$_3$H$_X$ species. In the end, about 2000 reactions (i.e. a little less than half of gas-phase reactions in current networks) have been investigated. All these results have been (or will be) put in the public on line database KIDA (http://kida.obs.u-bordeaux1.fr/). \\
In cold cores, the surface of interstellar grains play a role in this chemistry. This role was believed for several years to be dominated by the sticking of gas-phase species onto the surfaces of grains. At these very low temperatures, the diffusion of species on the surfaces and their subsequent reactions is assumed to be very limited. The thermal desorption of these species in the gas-phase is even less efficient. With the recent observation of complex molecules in the gas-phase in cold cores such as HCOOCH$_3$, CH$_3$OCH$_3$ and CH$_3$CHO (\cite{Bacmann_2012}, \cite{2014ApJ...795L...2V}), this belief has been questioned. Indeed, these species were up to now associated with warm star forming regions where the temperature would allow their formation on the grains and subsequent evaporation in the gas-phase (see \cite{Herbst_2009}). Now several scenario have been proposed to explain these observations and would need for testing to be validated (\cite{2013ApJ...769...34V}, \cite{2015MNRAS.449L..16B}, \cite{2015MNRAS.447.4004R}).



\begin{itemize}
\item{Cold core in the evolutionary context of the ISM}
\item{Cold temperature chemistry: COMs ?}
\item{Status of present work on chemistry in dense cores (TMC1, B1 ?), deep integrations of a few selected sources}
\end{itemize}
Need of systematic studies -> Survey
  
  
  
  
  
  
  
  
  
  
  